Allocation Removal by Partial Evaluation in a Tracing JIT

### 2010-10-14 talk/pepm2011/paper.tex
another comment by samuele
Add a comment
the escaping is not needed

@@

\begin{itemize}
    \item \lstinline{new} corresponds to object creation.
    \item \lstinline{get} correspond to attribute reads.
    \item \lstinline{set} correspond to attribute writes.
    \item \lstinline{guard\_class} correspond to method calls and are followed by
    the trace of the called method.
    \item \lstinline{int\_add} and \lstinline{int\_get} are integer addition and
    comparison (``greater than''), respectively.
\end{itemize}

@@

The trace shows the inefficiencies of \lstinline{f} clearly, if one looks at the
number of \lstinline{new}, \lstinline{set/get} and \lstinline{guard\_class} operations.
In the rest of the paper we will see how this trace can be optimized using
partial evaluation.

>>>>

XXX [fijal] I would say that the other goal of the JIT in case of dynamic
languages is to compile only a common scenario and leave a guard (instead
of proving that something will never ever happen)

@@

\begin{itemize}
    \item \lstinline{new} corresponds to object creation.
    \item \lstinline{get} correspond to attribute reads.
    \item \lstinline{set} correspond to attribute writes.
    \item \lstinline{guard_class} correspond to method calls and are followed by
    the trace of the called method.
    \item \lstinline{int_add} and \lstinline{int_get} are integer addition and
    comparison (``greater than''), respectively.
\end{itemize}

@@

The trace shows the inefficiencies of \lstinline{f} clearly, if one looks at the
number of \lstinline{new}, \lstinline{set/get} and \lstinline{guard_class} operations.
In the rest of the paper we will see how this trace can be optimized using
partial evaluation.

XXX add comment that guards are not only slow, but also use lots of memory
